Light Transport Techniques for Tensor Field Visualization

### 2019-08-11 beamer2thesis/dummy.tex
update

\frame{
\frametitle{{Light Transport Gradient (LTG) - Isotropic field}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{itemize}
	\item Isotropic test field reveals offset response for the approach
	\bigskip
	\item natural shift against the inital light source (slice) direction (left)\\
%	$\Rightarrow$ initial light source configurations located close and pointing towards borders, are biased for low LTG (FTLE) responses
\end{itemize}
\end{small}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\caption*{\textit{Isotropic test field}}\bigskip
\begin{minipage}{.49\textwidth}
\includegraphics[height=\textwidth]{isotropic2.png} \caption*{a)~Glyphs}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[height=\textwidth]{iso_ftle.png} \caption*{b)~LTG($0^\circ$)}
\end{minipage}

\end{figure}

\end{column}
\end{columns}

>>>>

\frame{
\frametitle{{Related Work - Symmetric Tensor Field Visualization}}

\begin{small}
\begin{itemize}
	\item glyphs\footnote[frame]{McLoughlin et al. ''Over two decades of integration-based, geometric flow visualization", 2010}: represent anisotropy with shape and orientation
	\item tensor field lines\footnote[frame]{Vilanova et al. ''Dti visualization with streamsurfaces beaand evenly-spaced volume seeding", 2004} (TFLs): follow tensor field along major eigenvector
	\item tensor field topology\footnote[frame]{Delmarcelle and Hesselink, “Visualizing second order tensor fields with hyperstreamlines”}: e.g. separatrices, degenerate points
	\item tensorlines\footnote[frame]{Weinstein et al. ''Tensorlines: Advection-diffusion
based propagation through diffusion tensor fields", 1999}: introduce artificial inertia to TFLs to increase stability
	\item HyperLIC\footnote[frame]{Zheng and Pang ''HyperLIC", 2003}: use Line Integral Convolution from vector field visualization on TFLs
	\item FTLE\footnote[frame]{Hlawatsch et al. ''Coherent structures of
characteristic curves in symmetric second order tensor fields", 2011}: exploit the gradient of the flow map of TFLs to generate an FTLE field
	\item scalar measures: fractional anisotropy\footnote[frame]{Basser ''Microstructural and physiological features of tissues elucidated by quantitative-diffusion-tensor MRI", 1996}, anisotropy coefficients\footnote[frame]{Westin et al. ''Geometrical
diffusion measures for MRI from tensor basis analysis", 2002}

\end{itemize}
\end{small}
